The pollination trade-off

### 2018-07-01 paper/questions_observations_todo.Rmd
Keep tex so I can use the same function to compile this as the others

---
title: "The pollination trade-off"
subtitle: "Workng doccument - questions & observations"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
date: "3/1/2018"
output: 
  bookdown::pdf_document2: 
    keep_tex: no
    number_sections: false
toc: false
header-includes:
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
---

@@

This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.
Marrero et al. 2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
Finally, Marrero et al. 2017 used pollen transfer networks and found that pollen diversity and pollination plant niche overlap (at the species level) is greater in agricultural communities. 
The increase on niche overlap was attributed to be positively associated with an increased abundance of exotic plants.

>>>>

---
title: "The pollination trade-off"
subtitle: "Workng doccument - questions & observations"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
date: "3/1/2018"
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
---

@@

This paper is almost entirely based on data that has already been published intidyr::separate units in Marrero et al. 2014, 2016, and 2017. 
Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.
Marrero et al. 2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
Finally, Marrero et al. 2017 used pollen transfer networks and found that pollen diversity and pollination plant niche overlap (at the species level) is greater in agricultural communities. 
The increase on niche overlap was attributed to be positively associated with an increased abundance of exotic plants.
